\documentclass[11pt]{article}
\usepackage[margin=1.0in]{geometry}
\usepackage{graphicx}
\usepackage[pdftex]{hyperref}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{sectsty}
\usepackage[document]{ragged2e}
\setlength\RaggedRightParindent{\parindent}
\usepackage{indentfirst}
\usepackage{changes}

\MakeOuterQuote{"}
\setlength\parindent{0.5in}
\setlist[itemize]{noitemsep}
\sectionfont{\fontsize{11}{10}\selectfont}
\pagenumbering{gobble} % No page number

\begin{document}

\begin{center}
    \textbf{Interview of Professional} \\
    Jonathan Sumner Evans \\
    \today
\end{center}

\section{Introduction}
% - Identify interviewee by name and job title and a brief description of job responsibilities.
%   (2-3 sentences)

I interviewed Bryan Evans, Senior Director Technical Resources Mine Engineering at Newmont Mining.
Bryan manages a group of engineers at Newmont's main corporate office\deleted{,} in
Greenwood Village. His group supports company projects, operations, \deleted{and}
mergers\added{,} and acquisitions. His group also provides corporate governance for mining
operation guidelines.

\section{Current Writing}
% - Time spent writing daily
% - Description of how writing is accomplished--any help from secretaries, co-workers, or technical
%   editors within their organization?

Currently, Bryan spends approximately 2.5 hours per day writing and another 4 reading other
people's work. Additionally he spends about 4 hours per week editing documents that other people
write. Currently, Bryan does not receive help from secretaries or technical writers as he writes,
but some of the people that work for him do. The types of documents that Bryan writes at his current
job include the following:

\begin{itemize}
    \item \textbf{Studies:} Efficiency, Research, Development\added{,} and Analytical
    \item \textbf{Standard Reports:} Inspection
    \item \textbf{Corporate:} Executive \replaced{s}{S}ummaries
    \item \textbf{Guides:} Procedures
    \item \textbf{Special Reports:} Recommendation and Trip
    \item \textbf{Technical Reports:} Feasibility
    \item \textbf{Interoffice:} Memos, Letters, Updates, Announcements, and Minutes
\end{itemize}

At previous positions, Bryan has written a variety of other documents including manuals and
marketing material.

\section{Career Development with Respect to Writing}
% - History of amount spent writing during various positions held in their career is given.
% - Description of professional's analysis of whether or not their writing skills have helped or
%   hindered their careers, and correlative positions held/not held described.
% - Description of attitude of various superiors throughout their career towards clear writing
%   skills

During his career, Bryan has changed roles from a consultant to a manager. In his managerial role he
does more peer reviewing of other people's work rather than writing technical documents himself.
Through his career, Bryan has had to develop his writing skills, \replaced{but}{and}, overall,
Bryan's writing skills have helped him advance his career. In his current managerial role, he has
read documents from people with exceptional writing skills which has caused him to develop a better
appreciation for good writing skills.

When asked about the importance of clear writing, Bryan explained that clear writing skills are
always critical for engineers so they can effectively communicate technical and work information. He
also has seen that people with poor writing skills are disadvantaged in the workplace.

\section{Summary}
% - Summary given by student of student's previous understanding of the importance of writing in the
%   professional workplace and new insights gained through the interview.

Since Bryan is my father, I had a general idea of the types of writing that he does at work, but
by interviewing him, I gained a greater understanding of the breadth of the writing that he does. I
was especially surprised at the amount of interoffice communication and studies that he writes.
Bryan gave a few examples of people with exemplary writing skills and how those skills have helped
their career development. Those examples helped illustrate the importance for engineers to have good
communication skills.

% MISC Requirements:
% - Document is organized, with clear subheadings for each question/portion of interview. Bulleted
%   lists and paragraphs used appropriately.
%
% - Excellent grammar, punctuation and spelling throughout the document; graphics are formatted
%   correctly and referred to in text, if used. (e.g. graph of typical day and time given to various
%   tasks)
%
% - Text is concise, informative, with little noise. Appropriate professional tone.

\end{document}
